\Huge \textbf{Hybrid rendering}\\ \huge using Radeon Rays

### 2018-10-29 Paper/Paper_BillietStijn_RadeonRays.tex
Altered order of certain stages to improve readability

\begin{minipage}{0.6\textwidth}
	The first task of the rasterizer is the homogeneous divide. The previous stages were in charge of transforming the vertices from model space into clipping space, this is done by multiplying the world, view and projection matrix with the vertices this yields a valid projection but does not account for depth information (f.e. objects that are nearby will appear the same as objects from afar) this is where the z-component comes in, seeing the z stores our depth information. Before we apply the projectionmatrix we store the z-component as an additional w component.
\end{minipage} \hfill
\begin{minipage}{0.4\textwidth}
	\includegraphics[width=\textwidth]{frustrum.png}
\end{minipage}
\vspace{0.2cm}

@@

\begin{minipage}{0.4\textwidth}
	\includegraphics[width=\textwidth]{pixelisation.png}
\end{minipage} \hfill
\begin{minipage}{0.55\textwidth}
	Rasterization(pixelisation) is the process of converting continuous primitives into discrete pixel fragments. The rasterizer does so by interpolating between vertex attributes (data that vertex holds) like color, normals, texture coordinates and positions. It then stores that information in the pixel fragments before finally sending it off to the pixel/fragment shader to be shaded.
\end{minipage}
\vspace{0.5cm}

>>>>

\begin{minipage}{0.59\textwidth}
	The first task of the rasterizer is the homogeneous divide. The previous stages were in charge of transforming the vertices from model space into clipping space, this is done by multiplying the world, view and projection matrix with the vertices this yields a valid projection but does not account for depth information (f.e. objects that are nearby will appear the same as objects from afar) this is where the z-component comes in, seeing the z stores our depth information. Before we apply the projectionmatrix we store the z-component as an additional w component.
\end{minipage} \hfill
\begin{minipage}{0.4\textwidth}
	\includegraphics[width=\textwidth]{frustrum.png}
\end{minipage}
\vspace{0.25cm}

@@

\begin{minipage}{0.4\textwidth}
	\includegraphics[width=0.8\textwidth]{culling.png}
\end{minipage} \hfill
\begin{minipage}{0.59\textwidth}
	The second task is the clipping stage, in this stage we clip triangles that lie (partly) outside of the view frustum. This effectively removes those triangles and prevents them from being projected/rendered. 
\end{minipage}

\vspace{0.5cm}

\begin{minipage}{0.55\textwidth}
	Rasterization(pixelisation) is the process of converting continuous primitives into discrete pixel fragments. The rasterizer does so by interpolating between vertex attributes (data that vertex holds) like color, normals, texture coordinates and positions. It then stores that information in the pixel fragments before finally sending it off to the pixel/fragment shader to be shaded.
\end{minipage} \hfill
\begin{minipage}{0.4\textwidth}
	\includegraphics[width=\textwidth]{pixelisation.png}
\end{minipage}
\vspace{0.5cm}
